The merger history of primordial-black-hole binaries implied by GWTC-3

### 2022-09-26 latex/paper.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% acknowledgments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
We thank the anonymous referee for providing constructive comments and suggestions to improve the quality of this paper. 
We would also like to thank Zu-Cheng Chen and Lang Liu for useful conversations.
This work is supported by grants from National Natural Science Foundation of China (grant No.11847107). 
This research has made use of data, software and/or web tools obtained 
from the Gravitational Wave Open Science Center \cite{Vallisneri:2014vxa}
(\url{https://www.gw-openscience.org}), a service of LIGO Laboratory, 
the LIGO Scientific Collaboration and the Virgo Collaboration. 
LIGO is funded by the U.S. National Science Foundation. 
Virgo is funded by the French Centre National de Recherche Scientifique (CNRS),
the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef,
with contributions by Polish and Hungarian institutes. 
\end{acknowledgments}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% acknowledgments %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgments}
% We thank the referee for providing constructive comments and suggestions to improve the quality of this paper. 
We would also like to thank Xingjiang Zhu, Shen-Shi Du for useful conversations.
This work is supported by grants from National Natural Science Foundation of China (grant No.11847107). 
This research has made use of data, software and/or web tools obtained 
from the Gravitational Wave Open Science Center \cite{Vallisneri:2014vxa}
(\url{https://www.gw-openscience.org}), a service of LIGO Laboratory, 
the LIGO Scientific Collaboration and the Virgo Collaboration. 
LIGO is funded by the U.S. National Science Foundation. 
Virgo is funded by the French Centre National de Recherche Scientifique (CNRS),
the Italian Istituto Nazionale della Fisica Nucleare (INFN) and the Dutch Nikhef,
with contributions by Polish and Hungarian institutes. 
\end{acknowledgments}
